### 2021-05-26 Manuscript/Jacobsville_manuscript.tex

This new age constraint on the Jacobsville provides crucial insight into the tectonic evolution of the Midcontinent Rift and the inversion of the extensional region into a compressional region due to the Grenville orogen. It also makes the Jacobsville sandstone a unique opportunity to investigate Laurentia's paleogeographical position at ca. 1 Ga as a long period of magmatic quiescence for $\sim$50 myr preceeds Jacobsville deposition left a gap in Laurentia apparent polar wander path between the Keweenawan Track and the Grenville Loop (Fig. xxx).

@@

Blake's current tectonic model: after MCR volcanics ca. 1084 Ma emplacement follows the deposition of the sediments (Oronto Group) copper harbor conglomerate, Nonesuch formation and the Freda formation. Then the Grenville orogenesis took off with the Ottawan phase from 1020 Ma - 10?? Ma and the Rigolet phase from 995-980 Ma. Paleosol development and the unconformity between the Jacobsville and the volcanics indicate a prolonged period of gap during which the Oronto Group in the backbulge basin where they were deposited were lost, resulting in younger Jacobsville deposition directly on top of the volcanics. The fact that in the Jacobsville has conglomerate and sandstone and siltstone facies in them supports sediment input from the eroded Oronto Group. This indicate the older boudnary of the Jacobsville deposition might be closer to the Rigolet Phase than the Ottowan phase. The younger age boundary of the Jacobsville is well defined - given that the maximum deposition age from the zircons of the Jacobsville is 993 Ma and the calcite on the Keweenaw Fault is 985.5 Ma, the deposition of at least the upper portion of the Jacobsville is well constrained to be between 993 and 985 Ma. The deposition of Jacobsville in the back bulge in Laurentia interior is related to the far-field compression caused by the Grenville Orogeny.

@@

>>>>

This new age constraint on the Jacobsville provides crucial insight into the tectonic evolution of the Midcontinent Rift and the inversion of the extensional region into a compressional region due to the Grenville orogen. It also makes the Jacobsville sandstone a unique opportunity to investigate Laurentia's paleogeographical position at ca. 1 Ga as a long period of magmatic quiescence for $\sim$50 myr precedes Jacobsville deposition left a gap in Laurentia apparent polar wander path between the Keweenawan Track and the Grenville Loop (Fig. xxx).

@@

Blake's current tectonic model: after MCR volcanics ca. 1084 Ma emplacement follows the deposition of the sediments (Oronto Group) copper harbor conglomerate, Nonesuch formation and the Freda formation. Then the Grenville orogenesis took off with the Ottawan phase from 1020 Ma - 10?? Ma and the Rigolet phase from 995-980 Ma. Paleosol development and the unconformity between the Jacobsville and the volcanics indicate a prolonged period of gap during which the Oronto Group in the backbulge basin where they were deposited were lost, resulting in younger Jacobsville deposition directly on top of the volcanics. The fact that in the Jacobsville has conglomerate and sandstone and siltstone facies in them supports sediment input from the eroded Oronto Group. This indicate the older boundary of the Jacobsville deposition might be closer to the Rigolet Phase than the Ottawan phase. The younger age boundary of the Jacobsville is well defined - given that the maximum deposition age from the zircons of the Jacobsville is 993 Ma and the calcite on the Keweenaw Fault is 985.5 Ma, the deposition of at least the upper portion of the Jacobsville is well constrained to be between 993 and 985 Ma. The deposition of Jacobsville in the back bulge in Laurentia interior is related to the far-field compression caused by the Grenville Orogeny.

@@

\subsection{Jacobsville stratigraphy}

Agate Falls

Natural Wall

Snake Creek

JK creek
